\Title

### 2016-02-14 manuscript/manuscript.tex
Caption for SAm inversion data figure
Caption for the SAm residuals figure

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-data}
    \caption{Input data for the inversion.
        (a) Sediment-free Bouguer disturbance for South America.
        (b) Map of seismic point estimates of Moho depth.}
    \label{fig:sam-data}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-moho}
    \caption{The estimated Moho of South America.}
    \label{fig:sam-moho}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/south-america-residuals}
    \caption{Residuals with histogram and convergence.}
    \label{fig:sam-residuals}
\end{figure}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-data}
    \caption{
        Input data for the South American Moho inversion.
        (a) Sediment-free Bouguer disturbance for South America.
        Obtained by subtracting the total sediment gravitational effect
        (Fig.~\ref{fig:sam-corrections}h) from the Bouguer disturbance
        (Fig.~\ref{fig:sam-corrections}d).
        (b) Seismological Moho depth estimates from
        \citet{assumpcao2012}.
    }
    \label{fig:sam-data}
\end{figure*}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-moho}
    \caption{
        Inversion results for the South American Moho.
        (a) The estimated Moho depth of South America.
        (b) Differences between the seismological depths of
        \citet{assumpcao2012} and our gravity-derived estimate shown in (a).
        The inset in (b) shows a histogram of the differences along with their
        calculated mean and standard deviation (std).
    }
    \label{fig:sam-moho}
\end{figure*}

\begin{figure}
    \centering
    \includegraphics{figures/south-america-residuals}
    \caption{
        Inversion residuals (observed data in Fig.~\ref{fig:sam-data}a
        minus the data predicted by the estimate in Fig.~\ref{fig:sam-moho}a)
        shown as (a) a map and (b) a histogram with the calculated mean and
        standard deviation.
        (c) The value of the goal function (Eq.~\ref{eq:goalfunction})
        per Gauss-Newton iteration showing the convergence of the algorithm.
        Note that the y-axis is in logarithmic scale.
    }
    \label{fig:sam-residuals}
\end{figure}
